Title

### 2023-06-23 main.tex
Otros cambios

Since their inception, quantum computers were proposed as powerful tools for
the simulation of quantum systems~\cite{feynman1982simulating}. 
% Several 
% kinds of quantum systems have been simulated, like \cpnote{PONER ALGO ACA Y CITAR. 
% Te puedes inspirar en las introducciones de articulos que simulen sistemas cuanticos}. 
Being open quantum systems of fundamental~\cite{Zur91,RevModPhys.76.1267} and
practical~\cite{breuer2007theory} interest, there has been efforts
towards the simulation of the evolution of open quantum
systems~\cite{cleve,Zanetti,Xin,Wei}\cpnote{porque escogiste estas citas? Me parece qeu la ce cleve no está completa.}.
Such systems have been simulated because of their many applications, 
such as studying the emergence of multipartite entanglement~\cite{Andrea,Andrea_AD},
studying dissipative processes~\cite{Barreiro}
and modeling non-Markovian dynamics~\cite{Marsden}.
Among quantum systems, the simplest case is that of a qubit~\cite{chuangbook},
and withing them, the simplest class of channels that produce decoherence are
Pauli channels~\cite{geometry,Zbigniew,Davalos}. Indeed, they serve as
effective models for the noise affecting quantum devices~\cite{Flammia,Fawzi}.

@@

We start by providing the definition of quantum channels, the general framework
used here, and multi-qubit Pauli channels in section \ref{sec: Pauli Channels}.
Our first objective is to present a quantum algorithm capable of simulating
Pauli channels on quantum computers; we do this in section \ref{sec: Circuit
for a Pauli Channel}, where we also demonstrate its implementation using IBM's
quantum computers for the particular case of single-qubit Pauli channels. 
Expanding beyond discrete Pauli channels, we introduce the concept of Pauli
dynamical maps, defined as a continuous parametrization of multi-qubit Pauli
channels.  Therefore, in section \ref{sec: 1PR Circuits} we shift our focus to
study parametrized quantum channels, aiming to adapt the algorithm developed
for channels to dynamical maps.  Furthermore, we contribute to the body of work
related to parametrized quantum circuits by establishing a theorem,
which  sets the mathematical conditions for the transformations
that can be done using a parametrized circuit with the condition that only a
controlled \cpnote{el caso general es controlado, correcto?} single-qubit
operation in the circuit may depend on the parameter.  Finally, in
section \ref{sec: 1PR circuit for a Pauli map}, we conclude about the Pauli
dynamical maps that fulfill the conditions of theorem \ref{theorem2}.

@@

Furthermore, we can construct other examples of 
Pauli dynamical maps such that they
can be implemented with a 1PR circuit.
To do it, we only need to choose the three states $|a\rangle$, $|b\rangle$, $|c\rangle$
that satisfy the conditions of  \eref{eq:conditions-vecs}.
For example, this can be done systematically for the case of curves of states of two qubits
(that is, for Pauli dynamical maps of one qubit)
with the following procedure:
\begin{itemize}
\item[1.] We first choose the norms $|a|$, $|b|$, $|c|$
such that $\langle a| a\rangle + \langle b| b\rangle + \langle c| c\rangle = 1$. 
This can be done by selecting two angles
$\mu \in [0, \pi/2]$, $\nu \in [0,\pi/2]$ and defining:
\begin{align*}
|a| = \sin \nu \cos \mu, \; |b| = \sin \nu \sin \mu , \; |c| = \cos \nu.
\end{align*}
\item[2.] We define $|a'\rangle = |a| |0\rangle$, $|b'\rangle = |b| |1\rangle$, $|c'\rangle = |c| |2\rangle$.
\item[3.] 
Finally, we choose a unitary matrix $V$ with the condition that its first
row is equal to $e^{i\theta} (|a|,|b|,|c|,0)$
with $\theta$ a uniform random phase.
That way, we can define $|a\rangle = V |a'\rangle$, $|b\rangle = V |b'\rangle$, $|c\rangle = V |c'\rangle$
and since $V$ is unitary, these unprimed vectors will fulfill the conditions of
\eref{eq:conditions-vecs}\cpnote{aun no construimos la $V$ asi que aun no es
unitaria. Aclarame ese punto y le sigo al resto del parrafo}.
Furthermore, the form of the first row ensures that the dynamical map begins at the identity,
since it implies that when $s=0$, the 
state created in \eref{eq:vec}
is
$|a\rangle + |b\rangle + |c\rangle = e^{i \theta} |0\rangle$,
which  corresponds with applying the identity channel.
Next, construct three vectors $\vec{w}_1 , \vec{w}_2, \vec{w}_3$ orthogonal to
the first row using the Gram-Schmidt process.  Then select random complex
numbers $r_1, r_2, r_3$ such that $|r_1|^2 + |r_2|^2 + |r_3|^2 = 1$ and define
the second row of $V$ to be $r_1 \vec{w}_1 + r_2 \vec{w}_2 + r_3 \vec{w}_3$.
Once the first two rows are chosen, use Gram-Schmidt to find two vectors
$\vec{v}_1, \vec{v}_2$ orthogonal to 
them and similarly define the third row as $q_1 \vec{v}_1+ q_2 \vec{v}_2$
with $|q_1|^2 + |q_2|^2$ and $q_1,q_2$
selected at random. 
Finally, there is only one choice for the fourth row so that it is 
orthonormal to the first three
and a random phase can be given to it.
\end{itemize}

@@

\cpnote{Reitera. Dale a lo qeu discutimos el espacio. a lo de la decoherencia nota
que no lo tomamos como un resultado importante. Aca le das mucho mas espacio 
del que croe que merece. Inspirate en la intro. }

{\color{purple}
In this work, we found a quantum algorithm for 
simulating Pauli channels in $N$-qubit systems and
generalized it to Pauli dynamical maps.
We observed that the fidelity of 
simulating single-qubit Pauli channels on one of IBM's quantum computers
was highest for those closest to the totally depolarizing channel and fell off close to unitary channels,
which was attributed to the current limitations of quantum computers.
Additionally, when working with Pauli dynamical maps,
we determined in theorem \ref{theorem2} the general mathematical conditions
under which a parametrized quantum circuit requires only one single-qubit rotation dependent on the parameter.

Therefore, this work presents another example of the current
exploration into simulating open quantum
systems in quantum computers,
and we observe the big effect that the error of quantum computers have
on these simulations.
On the other hand, the result
of theorem \ref{theorem2}
shows what can be done with the condition of using only one
parametrized rotation and
can be applied to any quantum algorithm that requires parametrized circuits,
such as those used for quantum machine learning.
}

>>>>

Since their inception, quantum computers were proposed as powerful tools for
the simulation of quantum systems~\cite{feynman1982simulating}. 
% Several 
% kinds of quantum systems have been simulated, like \cpnote{PONER ALGO ACA Y CITAR. 
% Te puedes inspirar en las introducciones de articulos que simulen sistemas cuanticos}. 
Being open quantum systems of fundamental~\cite{Zur91,RevModPhys.76.1267} and
practical~\cite{breuer2007theory} interest, there has been efforts
towards the simulation of the evolution of open quantum
systems~\cite{cleve,Zanetti,Xin,Wei}.\cpnote{porque escogiste estas citas? Me parece qeu la ce cleve no está completa.} \tbnote{La primera habla al principio en general
de simulación de sistemas abiertos y los otros tres porque se relacionan más con este trabajo
porque lo hacen en particular con el formalismo de canales cuánticos}
Such systems have been simulated because of their many applications, 
such as studying the emergence of multipartite entanglement~\cite{Andrea,Andrea_AD},
studying dissipative processes~\cite{Barreiro}
and modeling non-Markovian dynamics~\cite{Marsden}.
Among quantum systems, the simplest case is that of a qubit~\cite{chuangbook},
and withing them, the simplest class of channels that produce decoherence are
Pauli channels~\cite{geometry,Zbigniew,Davalos}. Indeed, they serve as
effective models for the noise affecting quantum devices~\cite{Flammia,Fawzi}.

@@

We start by providing the definition of quantum channels, the general framework
used here, and multi-qubit Pauli channels in section \ref{sec: Pauli Channels}.
Our first objective is to present a quantum algorithm capable of simulating
Pauli channels on quantum computers; we do this in section \ref{sec: Circuit
for a Pauli Channel}, where we also demonstrate its implementation using IBM's
quantum computers for the particular case of single-qubit Pauli channels. 
Expanding beyond discrete Pauli channels, we introduce the concept of Pauli
dynamical maps, defined as a continuous parametrization of multi-qubit Pauli
channels.  Therefore, in section \ref{sec: 1PR Circuits} we shift our focus to
study parametrized quantum channels, aiming to adapt the algorithm developed
for channels to dynamical maps.  Furthermore, we contribute to the body of work
related to parametrized quantum circuits by establishing a theorem,
which  sets the mathematical conditions for the transformations
that can be done using a parametrized circuit with the condition that only a
controlled \cpnote{el caso general es controlado, correcto?} \tbnote{Sí} single-qubit
operation in the circuit may depend on the parameter.  Finally, in
section \ref{sec: 1PR circuit for a Pauli map}, we conclude about the Pauli
dynamical maps that fulfill the conditions of theorem \ref{theorem2}.

@@

Furthermore, we can construct other examples of 
Pauli dynamical maps such that they
can be implemented with a 1PR circuit.
To do it, we only need to choose the three states $|a\rangle$, $|b\rangle$, $|c\rangle$
that satisfy the conditions of  \eref{eq:conditions-vecs}.
For example, this can be done systematically for the case of curves of states of two qubits
(that is, for Pauli dynamical maps of one qubit)
with the following procedure:
\begin{itemize}
\item[1.] We first choose the norms $|a|$, $|b|$, $|c|$
such that $\langle a| a\rangle + \langle b| b\rangle + \langle c| c\rangle = 1$. 
This can be done by selecting two angles
$\mu \in [0, \pi/2]$, $\nu \in [0,\pi/2]$ and defining:
\begin{align*}
|a| = \sin \nu \cos \mu, \; |b| = \sin \nu \sin \mu , \; |c| = \cos \nu.
\end{align*}
\item[2.] We define $|a'\rangle = |a| |0\rangle$, $|b'\rangle = |b| |1\rangle$, $|c'\rangle = |c| |2\rangle$.
\item[3.] 
Finally, we choose a unitary matrix $V$ with the condition that its first
row is equal to $e^{i\theta} (|a|,|b|,|c|,0)$
with $\theta$ a uniform random phase.
That way, we can define $|a\rangle = V |a'\rangle$, $|b\rangle = V |b'\rangle$, $|c\rangle = V |c'\rangle$
and since $V$ is unitary, these unprimed vectors will fulfill the conditions of
\eref{eq:conditions-vecs}\cpnote{aun no construimos la $V$ asi que aun no es
unitaria. Aclarame ese punto y le sigo al resto del parrafo}
\tbnote{Ah, es que más bien la idea era primero decir que el siguiente paso es
usar una matriz unitaria (con la condición
mencionada sobre el primer renglón)
y explicar cómo la usamos y por qué.
Ya luego mostrar cómo se puede construir dicha 
matriz al azar. También se puede hacer al revés,
pero no me convencía decir todo lo de cómo 
construir la matriz sin decir antes para qué}
.
Furthermore, the form of the first row ensures that the dynamical map begins at the identity,
since it implies that when $s=0$, the 
state created in \eref{eq:vec}
is
$|a\rangle + |b\rangle + |c\rangle = e^{i \theta} |0\rangle$,
which  corresponds with applying the identity channel.

Such a matrix $V$ can be randomly constructed by first finding three vectors 
$\vec{w}_1 , \vec{w}_2, \vec{w}_3$ orthogonal to
the first row using the Gram-Schmidt process.  Then selecting random complex
numbers $r_1, r_2, r_3$ such that $|r_1|^2 + |r_2|^2 + |r_3|^2 = 1$ and defining
the second row of $V$ to be $r_1 \vec{w}_1 + r_2 \vec{w}_2 + r_3 \vec{w}_3$.
Once the first two rows are chosen, use Gram-Schmidt to find two vectors
$\vec{v}_1, \vec{v}_2$ orthogonal to 
them and similarly define the third row as $q_1 \vec{v}_1+ q_2 \vec{v}_2$
with $|q_1|^2 + |q_2|^2$ and $q_1,q_2$
selected at random. 
Finally, there is only one choice for the fourth row so that it is 
orthonormal to the first three
and a random phase can be given to it.
\end{itemize}

@@

\cpnote{Reitera. Dale a lo qeu discutimos el espacio. a lo de la decoherencia nota
que no lo tomamos como un resultado importante. Aca le das mucho mas espacio 
del que croe que merece. Inspirate en la intro. }
\tbnote{Ah va, listo}

{\color{purple}
In this work, we found a quantum algorithm for 
simulating Pauli channels in $N$-qubit systems and
generalized it to Pauli dynamical maps
by using parametrized quantum circuits.
Furthermore, we implemented single-qubit Pauli channels
on one of IBM's quantum computers
and obtained their fidelities. 
Finally, when working with Pauli dynamical maps,
we searched for a way of simplifying the parametrized circuit
by requiring that only one single-qubit rotation depends on the parameter.
In theorem \ref{theorem2} we found the general mathematical conditions for 
this, applicable to any parametrized circuit.

Therefore, this work presents yet another example of the current
exploration into simulating open quantum
systems in quantum computers,
and we observe the big effect that the error of quantum computers have
on these simulations.
On the other hand, the result
of theorem \ref{theorem2}
shows what can be done with the condition of using only one
parametrized rotation and
can be applied to any quantum algorithm that requires parametrized circuits,
such as those used for quantum machine learning.
}
